Analyzing the impact of social attributes on commit integration success

### 2017-03-14 Paper/MSRChallenge2017.tex
quick spelling pass

\vspace{1ex}
\noindent\textbf{Technical Factors} We collected technical factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Source lines of source code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

\vspace{1ex}
\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate thecommit web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline
%
We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile:
%(\textit{https://github.com/\textbf{UserName}}). 
%

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience.
We also added one item from the MSR Challenge data set, indiating
whether the commit's developer is a core member  
of the associated project.

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifer that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train and present results for both
data sets individually.
\section{Evaluation}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

>>>>

\vspace{1ex}
\noindent\textbf{Technical Factors} We collected technical factors from the 
Mining Software Repositories (MSR) Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn, changed lines of code.
\item Files added by this commit.
\item Files modified by this commit.
\item Tests added by this commit.
\item Tests deleted by this commit.
\item Total source files in project at the time of the commit.
\item Source lines of source code in the project at
	the time of the commit.
\item Travis status, or status of the Travis build integration.
\end{itemize}

@@

\vspace{1ex}
\noindent\textbf{Social Factors.} We created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the
commit web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline
%
We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile:
%(\textit{https://github.com/\textbf{UserName}}). 
%

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience.
We also added one item from the MSR Challenge data set, indicating
whether the commit's developer is a core member  
of the associated project.

@@

74.43\% of the builds in the reduced dataset were successful, and thus a naive
classifier that always guesses ``successful'' would succeed 74.43\% of the time.
To penalize misclassification for
both classes equally, we created a second balanced dataset by randomly 
sub-sampling the successful builds until the two build status were
equal, a process known as downsampling.  We train and present results for both
data sets individually.
\section{Evaluation}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Non-Downsampled}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\
